Formalization of Abstract Rewriting

### 2025-11-05 Relations/Paper/Introduction.tex
Fixing urls

\subsection{Contributions}
Our contributions are as follows.
\begin{enumerate} \label{list:ourContributions}
  \item Formalization of elementary ARS theory as presented in
  \cite{Terese}, including relevant background; \sacomment{Should we remove this contribution as it is provided already in the agda standard library?}
  % Chapter 1 of
  \item An ontology of termination and confluence properties, and a detailed analysis of logical relationships between them;
  \item Definitions of new ARS concepts that refine our understanding of these relationships;
  \item Marginal improvements to classical confluence and termination criteria;
  \item An examination of several distinct notions of well-foundedness
  in the constructive setting.
\end{enumerate}

\subsection{Related works}
% We should cover the following in this section:
% \begin{itemize}
%   \item The IsaFoR/CeTA tool for certification of termination/confluence proofs provided by some automated tool (http://cl-informatik.uibk.ac.at/software/ceta/#introduction). Specifically this paper (https://www.isa-afp.org/entries/Abstract-Rewriting.html) deals with the formalization of strong normalization and Neman's lemma as part of the CeTA project. They use Isabelle for their formalization. 
%   \item This termination portal which gives an overview of various termination tools: https://termination-portal.org/wiki/Termination_Portal. Specifically here is a list of different termination tools: https://termination-portal.org/wiki/Category:Tools . We should talk about what distinguishes our project from a termination tool. 
%   \item Similarly this project is a collection of formalizations of theorems related to term rewrite systems in the language of the proof assistant PVS. http://trs.cic.unb.br/ (here is the formalization of Newman's lemma if you're interested! https://github.com/nasa/pvslib/blob/master/TRS/newman_yokouchi.pvs). 
%   \item Can nention that the agda standard library has a rewriting formalization too based on TeReSe
% \end{itemize}
Several formalizations of elementary ARS theory exist, including projects in Isabelle \cite{isabelleFormalization}, PVS \cite{trs}, and Coq \cite{coqARS}, as well as the Agda standard library \cite{AgdaLibraryRewriting}. Our work distinguishes itself through contributions 2-5 above: the detailed ontology of termination and confluence properties, new ARS concepts, refinements to classical criteria, and  examining multiple notions of well-foundedness.

>>>>

\subsection{Contributions}
Our contributions are as follows.
\begin{enumerate} \label{list:ourContributions}
  \item An original formalization of elementary ARS theory as presented in
  \cite{Terese}, including relevant background; 
  % Chapter 1 of
  \item An ontology of termination and confluence properties, and a detailed analysis of logical relationships between them;
  \item Definitions of new ARS concepts that refine our understanding of these relationships;
  \item Marginal improvements to classical confluence and termination criteria;
  \item An examination of several distinct notions of well-foundedness
  in the constructive setting.
\end{enumerate}

\subsection{Related works}
% We should cover the following in this section:
% \begin{itemize}
%   \item The IsaFoR/CeTA tool for certification of termination/confluence proofs provided by some automated tool (http://cl-informatik.uibk.ac.at/software/ceta/#introduction). Specifically this paper (https://www.isa-afp.org/entries/Abstract-Rewriting.html) deals with the formalization of strong normalization and Neman's lemma as part of the CeTA project. They use Isabelle for their formalization. 
%   \item This termination portal which gives an overview of various termination tools: https://termination-portal.org/wiki/Termination_Portal. Specifically here is a list of different termination tools: https://termination-portal.org/wiki/Category:Tools . We should talk about what distinguishes our project from a termination tool. 
%   \item Similarly this project is a collection of formalizations of theorems related to term rewrite systems in the language of the proof assistant PVS. http://trs.cic.unb.br/ (here is the formalization of Newman's lemma if you're interested! https://github.com/nasa/pvslib/blob/master/TRS/newman_yokouchi.pvs). 
%   \item Can nention that the agda standard library has a rewriting formalization too based on TeReSe
% \end{itemize}
Several formalizations of the concepts of elementary ARS theory exist, including projects in Isabelle \cite{isabelleFormalization}, PVS \cite{trs}, and Coq \cite{coqARS}, as well as the Agda standard library \cite{AgdaLibraryRewriting}. Our work distinguishes itself through contributions 2-5 above: the detailed ontology of termination and confluence properties, new ARS concepts, refinements to classical criteria, and  examining multiple notions of well-foundedness.
